### 2021-05-11 proposal/proposal.Rmd
updated proposal

### Subspace Clustering

@@

for some sparsity parameter $\lambda > 0$. The $c_i$ vectors are then collected into $C$ and $B$ as described before. If $X$ is noisy in that each $x_i$ does not lie exactly on one of $K$ subspaces but near it, the choice of $\lambda$ becomes important in guaranteeing the Subspace Detection Property (SDP) \cite{jmlr-v28-wang13}.

>>>>

@@

for some sparsity parameter $\lambda > 0$. The $c_i$ vectors are then collected into $C$ and $B$ as described before. If $X$ is noisy such that each $x_i$ does not lie exactly on one of $K$ subspaces but near it, the choice of $\lambda$ becomes important in guaranteeing the Subspace Detection Property (SDP) \cite{jmlr-v28-wang13}.

### 2021-05-11 proposal/proposal.tex
updated proposal

\hypertarget{subspace-clustering}{%
\subsubsection{Subspace Clustering}\label{subspace-clustering}}

@@

for some sparsity parameter \(\lambda > 0\). The \(c_i\) vectors are
then collected into \(C\) and \(B\) as described before. If \(X\) is
noisy in that each \(x_i\) does not lie exactly on one of \(K\)
subspaces but near it, the choice of \(\lambda\) becomes important in
guaranteeing the Subspace Detection Property (SDP)
\cite{jmlr-v28-wang13}.

>>>>

@@

for some sparsity parameter \(\lambda > 0\). The \(c_i\) vectors are
then collected into \(C\) and \(B\) as described before. If \(X\) is
noisy such that each \(x_i\) does not lie exactly on one of \(K\)
subspaces but near it, the choice of \(\lambda\) becomes important in
guaranteeing the Subspace Detection Property (SDP)
\cite{jmlr-v28-wang13}.
